Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-14 paper/paper.Rmd
Grammar edits

Figure \@ref(fig:ICFigs) Plot c contains a mosaic which allows consideration of the interaction between two image attributes. It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces. There are also no images that were taken at an upward angle with the background of the court.

This mosiac, Figure \@ref(fig:ICFigs) Plot d, allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring. As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd. The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.

@@

Considering the images used during our study were stills derived from Broadcast video files, it would be useful to extend further research to deal with the video files directly. The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.

@@

Given that Google found many faces that did not match manually annotated face,  manual errors were a possibility. To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.

Given that certain scene attribute combinations produced more facial recognition than other combinations a limit should be implemented for the sample of images sent to Google Vision API. This would not only reduce cost but also provide a greater level of detail of the emotions felt by a player during a match. To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed. This feed should match the scene attributes that provided the most Google faces.

@@

- Animetrics: This name used throughout the paper refers to the Animetrics Face Recognition API, FaceR API by @Animetrics.

- Google: @Google Refers to the Google Cloud Vision API

- Microsoft: This has been used to refer to the Microsoft Azure Cognitive Services Face API, published by @Microsoft.

- Skybiometry: @Skybiometry References the spin off detection and recognition software of Neurotechnology.

>>>>

Figure \@ref(fig:ICFigs) (c) contains a mosaic which allows consideration of the interaction between two image attributes. It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces. There are also no images that were taken at an upward angle with the background of the court.

This mosiac, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring. As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd. The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.

@@

Considering the images used during our study were stills derived from broadcast video files, it would be useful to extend further research to deal with the video files directly. The Google Vision API which produced the best recognition in images does not yet have the potential to detect faces and emotions in a video.

@@

Google found many faces that did not match manually annotated faces, this showed manual errors were a possibility. To search for these Taipan could be extended to allow the face identified to be displayed and confirmed this would allow the annotator to confirm manually whether or not these are faces.

Given that certain scene attribute combinations produced more successful facial recognition than other combinations, a limit should be implemented for the sample of images sent to Google Vision API. This would not help to reduce cost. To provide a greater level of information at all points in a match it would be beneficial to derive images from a single camera feed. This feed should match the scene attributes that provided was most successful for Google to return faces.

@@

- Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.

- Google: Google Cloud Vision API [-@Google]

- Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.

- Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology.
